Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
add ml mention

# Results
<!-- TODO intro + ml fig -->

Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength
decreased. GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] 
us to confirm the use of 50 m buffer that has long been used
for studies in the field [@Lingle_2003; @Clutton_1982].

@@

>>>>

# Results
Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength
decreased. GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] 
us to confirm the use of 50 m buffer that has long been used
for studies in the field [@Lingle_2003; @Clutton_1982].

@@

An illustrative multilayer network was generated, informed by previous social, 
spatial and temporal scale results (Figure \@ref(fig:ml)). <!--The social 
distance threshold was 50 m. The spatial resolution of the land cover 
raster was 30 m. -->Relocations were predominantly in open 
(`r count[res == 30 & lc == 1, percent]`%) and forest 
(`r count[res == 30 & lc == 2, percent]`%) habitats 
compared to foraging habitats (`r count[res == 30 & lc == 3, percent]`%). 
Despite this, individuals were more strongly connected in foraging and open 
habitats than in forest (mean graph strength in habitat layers; foraging: 0.21, 
forest: 0.11, open: 0.23). There was a seasonal difference in association, 
individuals were more connected between approximately October - June 
(mean graph strength in time windows; 2: 0.37, 4: 0.18) 
than between approximately June - October 
(mean graph strength in time windows; 1: 0.04, 3: 0.03).
